%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

%----------------------------------------------------------------------------------------
%	PERSONAL INFO SECTION
%----------------------------------------------------------------------------------------

\name{Em Tarrant}
\address{entarrant@gmail.com \\ 512 709 1062}

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

%-------------------Leafly--------------------

\begin{rSubsection}{Leafly}{May 2022 - Present}{Senior Software Engineer}{Remote}
\item Rearchitected dispensary hours schedule data model from denormalized JSONB columns into dedicated normalized database table. Led team of
three other engineers to migrate usage of the old model to the new model across seven repositories. Implemented backfill logic from the new model
to the old model to allow for gradual strategic updates.
\item Contributed to team direction as technical lead by advocating for resolution of customer pain points, writing and executing technical project plans,
and coordinating with Product Manager to determine the most valuable and achievable project requirements.
\item Implemented team process for business hours on-call rotation. Created document detailing team member responsibilities for responding to alerts and
production bugs, as well as carving out dedicated time for addressing technical debt and dependency updates.
\end{rSubsection}

%-------------------project44--------------------

\begin{rSubsection}{project44}{August 2021 - May 2022}{Senior Software Engineer}{Austin, TX}
\item Developed API endpoints to allow retailers to customize their tracking page and shipment alert experiences, reducing the
amount of manual engineering intervention to onboard a customer and decreasing implementation time by half a day.
\item Aided in regression testing the platform during a major upgrade of the project44 design system, decreasing the amount of
testing the Product team was responsible for and unblocking frontend engineers by providing timely and thorough feedback.
\item Increased attendance of refinement meetings allowing all team members to participate, resulting in better knowledge transfer,
ticket implementation time, and collaboration.
\end{rSubsection}

%------------------BigCommerce-------------------

\begin{rSubsection}{BigCommerce}{August 2018 - August 2021}{Software Engineer}{Austin, TX}
\item Collaborated on the planning and development of two-step verification (2SV) for merchants. Worked on proof of concept for
Authy integration that laid the ground work for two-factor authentication (2FA) project.
\item Implemented VAT tax feature on Billing Platform application to allow for the proper taxing of European merchants in their billing
statements, requiring coordination with product manager to ensure adherence to the relevant tax laws.
\item Mentored and onboarded product and engineering team members.
\end{rSubsection}

%-------------------Spiceworks-------------------

\begin{rSubsection}{Spiceworks}{July 2015 - August 2018}{Software Engineer}{Austin, TX}
\item Designed and implemented backend streaming service and APIs for the Community Activity Feed resulting in the first versioned internal
Spiceworks API. Coordinated with frontend engineers and project managers to determine Feed product direction as primary contributor.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages/Frameworks \\
Proficient & Ruby, Rails, RSpec \\
Experienced & JavaScript, Typescript, Node, React, Java \\
Exposure & Kotlin, Android, Scala
Technologies & PostgreSQL, Redis, Sidekiq, Datadog, CI/CD Pipelines, Containers

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf University of Texas at Austin} \\
Bachelor of Science in Computer Science, GPA 3.48
\end{rSection}

\end{document}
